Settler colonial projects and variation in paths to building the welfare and carceral state

### 2023-11-21 t1_analysis.Rmd
work on shapefiles and on morill data

### land grab u data
# lgu_cessions<-read_csv("./data/landgrabu-data/Morrill_Act_of_1862_Indigenous_Land_Parcels_Database/CSVs/Cessions.csv")
### this is cessions from the Royce maps, overlaps with morrill, but includes prior cessions as well
### would need to use shapefiles to portion out by state
lgu_parcels<-read_csv("./data/landgrabu-data/Morrill_Act_of_1862_Indigenous_Land_Parcels_Database/CSVs/Parcels.csv")
lgu_unis<-read_csv("./data/landgrabu-data/Morrill_Act_of_1862_Indigenous_Land_Parcels_Database/CSVs/Universities.csv")
```

>>>>

### land grab u data
# lgu_cessions<-read_csv("./data/landgrabu-data/Morrill_Act_of_1862_Indigenous_Land_Parcels_Database/CSVs/Cessions.csv")
### this is cessions from the Royce maps, overlaps with morrill, but includes prior cessions as well
### would need to use shapefiles to portion out by state
lgu_parcels<-read_csv("./data/landgrabu-data/Morrill_Act_of_1862_Indigenous_Land_Parcels_Database/CSVs/Parcels.csv")
```
